%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Data Integration Developer} % Job title
    {Tucows} % Organization
    {Toronto, Ontario, Canada} % Location
    {July. 2010 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, build, secure, implement and maintain Data ETL platform with DBT, Airflow, Kafka and Snowflake}
        \item {Build automation to provision, maintain, and monitor all aspects of Kafka, Airflow and AWS SageMaker  environment via infrastructure as code.}
        \item {Successful  migration of on-premise data ETL job orchestration system (Airflow) to AWS managed Airflow}
        \item {Administered Data Lake (Snowflake) using Terraform}
        \item {Deployed AWS Python Lambdas to create and deliver usage reports }
        \item {Implemented CI/CD for Machine learning Pipelines using Terraform and AWS SageMaker}
        \item { Used Terraform, SaltStack, GitHub Actions etc. to implement CI/CD pipelines for Kafka and Airflow}
        \item {Conceived and wrote detailed software implementations while ensuring that their code adhere to the security, logging, error handling, and performance standards and non-functional requirements.}
        \vspace{1mm} %1mm vertical space
        \item {\textbf{Skills}:Application Development(Python, Java, KafkaStreams, KafkaConnect, JUnit),AWS (IAM, S3, Lambda, Managed Airflow, SageMaker, SQS, SNS, CloudWatch, CloudFormation) Other(Terraform, Docker, SaltStack, Airflow, DBT, Snowflake, GitHub Actions, Jira, Confluence, Asana).}
      \end{cvitems}
    }
    \vspace{5mm} %5mm vertical space
%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {BMO Financial Group} % Organization
    {Toronto, Ontario, Canada} % Location
    {Jan. 2020 - Juky 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, build, secure, implement and maintain Multi-data-center Kafka infrastructure.}
        \item {Build automation to provision, maintain, and monitor all aspects of the Kafka environment via infrastructure as code.}
        \item To meet stringent Recovery Point Objective (RPO), converted traditional Kafka clusters to multi region clusters. 
        \item {Helped build real-time streaming data pipelines to reliably get data between systems and applications.}
        \item {Identify bottlenecks and tune to optimize Kafka performance and throughput.}
        \item {Built real-time streaming applications Kafka streams that transform \& react to streams of data.}
        \item {Conceived and wrote detailed software implementations while ensuring that their code adhere to the security, logging, error handling, and performance standards and non-functional requirements.}
        \item {Automating on-boarding of clients to Kafka by developing CI/CD pipelines for Kafka Streams, Topics, ACLs, Schemas, Kafka Connectors etc.}
         \vspace{1mm} %1mm vertical space
        \item {\textbf{Skills}:Application Development(Java, KafkaStreams, KafkaConnect, JUnit), Other(JSON, AVRO, WSDL, HTML, CSS3, JavaScript, Angular, Git, Ansible, Bamboo, Jira, Confluence).}
      \end{cvitems}
    }
    \vspace{5mm} %5mm vertical space
%---------------------------------------------------------
  \cventry
    {Software Developer (Contract)} % Job title
    {Orbis Communications} % Organization
    {Hamilton, Ontario, Canada} % Location
    {Oct. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhancement \& bug fixes in Java based backend.}
        \item { Frontend changes using JavaScript, jQuery and CSS }
        \vspace{1mm} %1mm vertical space
        \item {\textbf{Skills}:Application Development(Java, Spring, JSP, Hibernate, SQL, JUnit,
        jQuery, JavaScript, HTML/CSS), Scripting(Bash, Python), Other(BitBucket, Jira, HTML/CSS).}
      \end{cvitems}
    }
    \vspace{5mm} %5mm vertical space
%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {TD Bank} % Organization
    {Toronto, Ontario, Canada} % Location
    {Mar. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design \& Develop Spring Batch jobs in Java using dependency management and build tool Maven.}
        \item {REST API development using JAVA 8, Spring Boot, Spring, JPA/Hibernate and unit tests.}
        \item {Develop SQL stored procedures to perform data intensive logic and Shell Scripts for file manipulation, Job dependencies etc. }
        \item {Cross-communicated between development teams to design blueprints of common Java classes and ensure they would perform correctly upon completion}
        \item {Excellent time-management and multi-tasking skills through simultaneous tight deadline driven projects and tasks.}
        \vspace{1mm} %1mm vertical space
        \item {\textbf{Skills}:Application Development(Java, Spring Batch, JDBC, Hibernate, JUnit), Scripting (Bash, Python), Other(Jenkins, Bitbucket, SonarQube, Confluence, Jira, HTML/CSS).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}